---
title: "Visualizations for CDC 2024"
output:
  pdf_document: default
date: "2024-09-28"
---
Import Libraries
```{r setup, include=FALSE}
#This code chunk is for modifying the global options and for loading required R packages
knitr::opts_chunk$set(echo = TRUE)
library(rmarkdown)
library(tinytex)
library(knitr)
library(readr)
library(mosaic) #Install Mosaic Package
library(Stat2Data) #Install Stat2Data
library(MASS) # You may need to install this package
```

Read in Cleaned Data
```{r}
DT <- read_csv("Datasets/Death_And_Trips_Per_State.csv")
head(DT)
```

California Stats
 
California Covid Deaths vs Local Travel
```{r}
CA = DT[DT$Jurisdiction == 'California',]
head(CA)

model <- lm(CA$Local_Trips ~ CA$Covid_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of California Covid Deaths vs Local Travel")
qqline(model$residuals)
CA$CookD = cooks.distance(model)
CAC <- CA[which(CA$CookD < 0.5),]
bc <- boxcox(CAC$Local_Trips ~ CAC$Covid_Deaths)
lambda <- bc$x[which.max(bc$y)]
CAC$Local_Trips1 <- (((CAC$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(CAC$Local_Trips1 ~ CAC$Covid_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(CAC$Local_Trips1 ~ CAC$Covid_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```
California Influenza Deaths vs Local Travel
```{r}
model <- lm(CA$Local_Trips ~ CA$Influenza_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of California Influenza Deaths vs Local Travel")
qqline(model$residuals)
CA$CookD = cooks.distance(model)
CAI <- CA[which(CA$CookD < 0.5),]
bc <- boxcox(CAI$Local_Trips ~ CAI$Influenza_Deaths)
lambda <- bc$x[which.max(bc$y)]
CAI$Local_Trips1 <- (((CAI$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(CAI$Local_Trips1 ~ CAI$Influenza_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(CAI$Local_Trips1 ~ CAI$Influenza_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```
California Covid Deaths vs Interstate Travel
```{r}
model <- lm(CA$Interstate_Trips ~ CA$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of California Covid Deaths vs Inter Travel")
qqline(model$residuals) 
CA$CookD = cooks.distance(model) 
CAC <- CA[which(CA$CookD < 0.5),]
bc <- boxcox(CAC$Interstate_Trips ~ CAC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
CAC$Interstate_Trips1 <- (((CAC$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(CAC$Interstate_Trips1 ~ CAC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(CAC$Interstate_Trips1 ~ CAC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals) 
```
California Influenza Deaths vs Interstate Travel
```{r}
model <- lm(CA$Interstate_Trips ~ CA$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of California Influenza Deaths vs Inter Travel") 
qqline(model$residuals) 
CA$CookD = cooks.distance(model) 
CAI <- CA[which(CA$CookD < 0.5),] 
bc <- boxcox(CAI$Interstate_Trips ~ CAI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
CAI$Interstate_Trips1 <- (((CAI$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(CAI$Interstate_Trips1 ~ CAI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(CAI$Interstate_Trips1 ~ CAI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```
California Covid Deaths vs Long Distance Trips
```{r}
model <- lm(CA$Long_Distance_Trips ~ CA$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of California Covid Deaths vs Long Travel")
qqline(model$residuals) 
CA$CookD = cooks.distance(model) 
CAC <- CA[which(CA$CookD < 0.5),]
bc <- boxcox(CAC$Long_Distance_Trips ~ CAC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
CAC$Long_Distance_Trips1 <- (((CAC$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(CAC$Long_Distance_Trips1 ~ CAC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(CAC$Long_Distance_Trips1 ~ CAC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals) 
```

California Influenza Deaths vs Long Distance Trips
```{r}
model <- lm(CA$Long_Distance_Trips ~ CA$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of California Influenza Deaths vs Long Travel") 
qqline(model$residuals) 
CA$CookD = cooks.distance(model) 
CAI <- CA[which(CA$CookD < 0.5),] 
bc <- boxcox(CAI$Long_Distance_Trips ~ CAI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
CAI$Long_Distance_Trips1 <- (((CAI$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(CAI$Long_Distance_Trips1 ~ CAI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(CAI$Long_Distance_Trips1 ~ CAI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

North Carolina Stats
 
North Carolina Covid Deaths vs Local Trips
```{r}
NC = DT[DT$Jurisdiction == 'North Carolina',]
head(NC)

model <- lm(NC$Local_Trips ~ NC$Covid_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of North Carolina Covid Deaths vs Local Travel")
qqline(model$residuals)
NC$CookD = cooks.distance(model)
NCC <- NC[which(NC$CookD < 0.5),]
bc <- boxcox(NCC$Local_Trips ~ NCC$Covid_Deaths)
lambda <- bc$x[which.max(bc$y)]
NCC$Local_Trips1 <- (((NCC$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(NCC$Local_Trips1 ~ NCC$Covid_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(NCC$Local_Trips1 ~ NCC$Covid_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```

North Carolina Influenza Deaths vs Local Trips
```{r}
model <- lm(NC$Local_Trips ~ NC$Influenza_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of North Carolina Influenza Deaths vs Local Travel")
qqline(model$residuals)
NC$CookD = cooks.distance(model)
NCI <- NC[which(NC$CookD < 0.5),]
bc <- boxcox(NCI$Local_Trips ~ NCI$Influenza_Deaths)
lambda <- bc$x[which.max(bc$y)]
NCI$Local_Trips1 <- (((NCI$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(NCI$Local_Trips1 ~ NCI$Influenza_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(NCI$Local_Trips1 ~ NCI$Influenza_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```

North Carolina Covid Deaths vs Interstate Trips
```{r}
model <- lm(NC$Interstate_Trips ~ NC$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of North Carolina Covid Deaths vs Interstate Travel")
qqline(model$residuals) 
NC$CookD = cooks.distance(model) 
NCC <- NC[which(NC$CookD < 0.5),]
bc <- boxcox(NCC$Interstate_Trips ~ NCC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
NCC$Interstate_Trips1 <- (((NCC$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(NCC$Interstate_Trips1 ~ NCC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(NCC$Interstate_Trips1 ~ NCC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals) 
```

North Carolina Influenza Deaths vs Interstate Trips
```{r}
model <- lm(NC$Interstate_Trips ~ NC$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of North Carolina Influenza Deaths vs Interstate Travel") 
qqline(model$residuals) 
NC$CookD = cooks.distance(model) 
NCI <- NC[which(NC$CookD < 0.5),] 
bc <- boxcox(NCI$Interstate_Trips ~ NCI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
NCI$Interstate_Trips1 <- (((NCI$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(NCI$Interstate_Trips1 ~ NCI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(NCI$Interstate_Trips1 ~ NCI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

North Carolina Covid Deaths vs Long Distance Trips
```{r}
model <- lm(NC$Long_Distance_Trips ~ NC$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of North Carolina Covid Deaths vs Long_Distance Travel")
qqline(model$residuals) 
NC$CookD = cooks.distance(model) 
NCC <- NC[which(NC$CookD < 0.5),]
bc <- boxcox(NCC$Long_Distance_Trips ~ NCC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
NCC$Long_Distance_Trips1 <- (((NCC$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(NCC$Long_Distance_Trips1 ~ NCC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(NCC$Long_Distance_Trips1 ~ NCC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals) 
```

North Carolina Influenza Deaths vs Long Distance Trips
```{r}
model <- lm(NC$Long_Distance_Trips ~ NC$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of North Carolina Influenza Deaths vs Long_Distance Travel") 
qqline(model$residuals) 
NC$CookD = cooks.distance(model) 
NCI <- NC[which(NC$CookD < 0.5),] 
bc <- boxcox(NCI$Long_Distance_Trips ~ NCI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
NCI$Long_Distance_Trips1 <- (((NCI$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(NCI$Long_Distance_Trips1 ~ NCI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(NCI$Long_Distance_Trips1 ~ NCI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

Georgia Stats

Georgia Covid Deaths vs Local Trips
```{r}
GA = DT[DT$Jurisdiction == 'Georgia',]
head(GA)

model <- lm(GA$Local_Trips ~ GA$Covid_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of Georgia Covid Deaths vs Local Travel")
qqline(model$residuals)
GA$CookD = cooks.distance(model)
GAC <- GA[which(GA$CookD < 0.5),]
bc <- boxcox(GAC$Local_Trips ~ GAC$Covid_Deaths)
lambda <- bc$x[which.max(bc$y)]
GAC$Local_Trips1 <- (((GAC$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(GAC$Local_Trips1 ~ GAC$Covid_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(GAC$Local_Trips1 ~ GAC$Covid_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```

Georgia Influenza Deaths vs Local Trips
```{r}
model <- lm(GA$Local_Trips ~ GA$Influenza_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of Georgia Influenza Deaths vs Local Travel")
qqline(model$residuals)
GA$CookD = cooks.distance(model)
GAI <- GA[which(GA$CookD < 0.5),]
bc <- boxcox(GAI$Local_Trips ~ GAI$Influenza_Deaths)
lambda <- bc$x[which.max(bc$y)]
GAI$Local_Trips1 <- ((GAI$Local_Trips^lambda - 1) / lambda)
new_model <- lm(GAI$Local_Trips1 ~ GAI$Influenza_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(GAI$Local_Trips1 ~ GAI$Influenza_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```

Georgia Covid Deaths vs Interstate Trips
```{r}
model <- lm(GA$Interstate_Trips ~ GA$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Georgia Covid Deaths vs Interstate Travel")
qqline(model$residuals) 
GA$CookD = cooks.distance(model) 
GAC <- GA[which(GA$CookD < 0.5),]
bc <- boxcox(GAC$Interstate_Trips ~ GAC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
GAC$Interstate_Trips1 <- (((GAC$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(GAC$Interstate_Trips1 ~ GAC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(GAC$Interstate_Trips1 ~ GAC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

Georgia Influenza Deaths vs Interstate Trips
```{r}
model <- lm(GA$Interstate_Trips ~ GA$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Georgia Influenza Deaths vs Interstate Travel") 
qqline(model$residuals) 
GA$CookD = cooks.distance(model) 
GAI <- GA[which(GA$CookD < 0.5),] 
bc <- boxcox(GAI$Interstate_Trips ~ GAI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
GAI$Interstate_Trips1 <- (((GAI$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(GAI$Interstate_Trips1 ~ GAI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(GAI$Interstate_Trips1 ~ GAI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

Georgia Covid Deaths vs Long Distance Trips
```{r}
model <- lm(GA$Long_Distance_Trips ~ GA$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Georgia Covid Deaths vs Long_Distance Travel")
qqline(model$residuals) 
GA$CookD = cooks.distance(model) 
GAC <- GA[which(GA$CookD < 0.5),]
bc <- boxcox(GAC$Long_Distance_Trips ~ GAC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
GAC$Long_Distance_Trips1 <- (((GAC$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(GAC$Long_Distance_Trips1 ~ GAC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(GAC$Long_Distance_Trips1 ~ GAC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

Georgia Influenza Deaths vs Long Distance Trips
```{r}
model <- lm(GA$Long_Distance_Trips ~ GA$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Georgia Influenza Deaths vs Long_Distance Travel") 
qqline(model$residuals) 
GA$CookD = cooks.distance(model) 
GAI <- GA[which(GA$CookD < 0.5),] 
bc <- boxcox(GAI$Long_Distance_Trips ~ GAI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
GAI$Long_Distance_Trips1 <- (((GAI$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(GAI$Long_Distance_Trips1 ~ GAI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(GAI$Long_Distance_Trips1 ~ GAI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

New York Stats

New York Covid Deaths vs Local Trips
```{r}
NY = DT[DT$Jurisdiction == 'New York',]
head(NY)

model <- lm(NY$Local_Trips ~ NY$Covid_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of New York Covid Deaths vs Local Travel")
qqline(model$residuals)
NY$CookD = cooks.distance(model)
NYC <- NY[which(NY$CookD < 0.5),]
bc <- boxcox(NYC$Local_Trips ~ NYC$Covid_Deaths)
lambda <- bc$x[which.max(bc$y)]
NYC$Local_Trips1 <- (((NYC$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(NYC$Local_Trips1 ~ NYC$Covid_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(NYC$Local_Trips1 ~ NYC$Covid_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```

New York Influenza Deaths vs Local Trips
```{r}
model <- lm(NY$Local_Trips ~ NY$Influenza_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of New York Influenza Deaths vs Local Travel")
qqline(model$residuals)
NY$CookD = cooks.distance(model)
NYI <- NY[which(NY$CookD < 0.5),]
bc <- boxcox(NYI$Local_Trips ~ NYI$Influenza_Deaths)
lambda <- bc$x[which.max(bc$y)]
NYI$Local_Trips1 <- (((NYI$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(NYI$Local_Trips1 ~ NYI$Influenza_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(NYI$Local_Trips1 ~ NYI$Influenza_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```

New York Covid Deaths vs Interstate Trips
```{r}
model <- lm(NY$Interstate_Trips ~ NY$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of New York Covid Deaths vs Interstate Travel")
qqline(model$residuals) 
NY$CookD = cooks.distance(model) 
NYC <- NY[which(NY$CookD < 0.5),]
bc <- boxcox(NYC$Interstate_Trips ~ NYC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
NYC$Interstate_Trips1 <- (((NYC$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(NYC$Interstate_Trips1 ~ NYC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(NYC$Interstate_Trips1 ~ NYC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

New York Influenza Deaths vs Interstate Trips
```{r}
model <- lm(NY$Interstate_Trips ~ NY$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of New York Influenza Deaths vs Interstate Travel") 
qqline(model$residuals) 
NY$CookD = cooks.distance(model) 
NYI <- NY[which(NY$CookD < 0.5),] 
bc <- boxcox(NYI$Interstate_Trips ~ NYI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
NYI$Interstate_Trips1 <- (((NYI$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(NYI$Interstate_Trips1 ~ NYI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(NYI$Interstate_Trips1 ~ NYI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

New York Covid Deaths vs Long Distance Trips
```{r}
model <- lm(NY$Long_Distance_Trips ~ NY$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of New York Covid Deaths vs Long_Distance Travel")
qqline(model$residuals) 
NY$CookD = cooks.distance(model) 
NYC <- NY[which(NY$CookD < 0.5),]
bc <- boxcox(NYC$Long_Distance_Trips ~ NYC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
NYC$Long_Distance_Trips1 <- (((NYC$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(NYC$Long_Distance_Trips1 ~ NYC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(NYC$Long_Distance_Trips1 ~ NYC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

New York Influenza Deaths vs Long Distance Trips
```{r}
model <- lm(NY$Long_Distance_Trips ~ NY$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of New York Influenza Deaths vs Long_Distance Travel") 
qqline(model$residuals) 
NY$CookD = cooks.distance(model) 
NYI <- NY[which(NY$CookD < 0.5),] 
bc <- boxcox(NYI$Long_Distance_Trips ~ NYI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
NYI$Long_Distance_Trips1 <- (((NYI$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(NYI$Long_Distance_Trips1 ~ NYI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(NYI$Long_Distance_Trips1 ~ NYI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

Wyoming Stats

Wyoming Covid Deaths vs Local Trips
```{r}
WY = DT[DT$Jurisdiction == 'Wyoming',]
head(WY)

model <- lm(WY$Local_Trips ~ WY$Covid_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of Wyoming Covid Deaths vs Local Travel")
qqline(model$residuals)
WY$CookD = cooks.distance(model)
WYC <- WY[which(WY$CookD < 0.5),]
bc <- boxcox(WYC$Local_Trips ~ WYC$Covid_Deaths)
lambda <- bc$x[which.max(bc$y)]
WYC$Local_Trips1 <- (((WYC$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(WYC$Local_Trips1 ~ WYC$Covid_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(WYC$Local_Trips1 ~ WYC$Covid_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```

Wyoming Covid Deaths vs Interstate Trips
```{r}
model <- lm(WY$Interstate_Trips ~ WY$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Wyoming Covid Deaths vs Interstate Travel")
qqline(model$residuals) 
WY$CookD = cooks.distance(model) 
WYC <- WY[which(WY$CookD < 0.5),]
bc <- boxcox(WYC$Interstate_Trips ~ WYC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
WYC$Interstate_Trips1 <- (((WYC$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(WYC$Interstate_Trips1 ~ WYC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(WYC$Interstate_Trips1 ~ WYC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals) 
```

Wyoming Covid Deaths vs Long Distance Trips
```{r}
model <- lm(WY$Long_Distance_Trips ~ WY$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Wyoming Covid Deaths vs Long_Distance Travel")
qqline(model$residuals) 
WY$CookD = cooks.distance(model) 
WYC <- WY[which(WY$CookD < 0.5),]
bc <- boxcox(WYC$Long_Distance_Trips ~ WYC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
WYC$Long_Distance_Trips1 <- (((WYC$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(WYC$Long_Distance_Trips1 ~ WYC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(WYC$Long_Distance_Trips1 ~ WYC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals) 
```

Wyoming had no Influenza Deaths

Florida Stats

Florida Covid Deaths vs Local Trips
```{r}
FL = DT[DT$Jurisdiction == 'Florida',]
head(FL)

model <- lm(FL$Local_Trips ~ FL$Covid_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of Florida Covid Deaths vs Local Travel")
qqline(model$residuals)
FL$CookD = cooks.distance(model)
FLC <- FL[which(FL$CookD < 0.5),]
bc <- boxcox(FLC$Local_Trips ~ FLC$Covid_Deaths)
lambda <- bc$x[which.max(bc$y)]
FLC$Local_Trips1 <- (((FLC$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(FLC$Local_Trips1 ~ FLC$Covid_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(FLC$Local_Trips1 ~ FLC$Covid_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```

Florida Influenza Deaths vs Local Trips
```{r}
model <- lm(FL$Local_Trips ~ FL$Influenza_Deaths)
qqnorm(model$residuals, main = "Normal Q-Q Plot of Florida Influenza Deaths vs Local Travel")
qqline(model$residuals)
FL$CookD = cooks.distance(model)
FLI <- NY[which(NY$CookD < 0.5),]
bc <- boxcox(FLI$Local_Trips ~ FLI$Influenza_Deaths)
lambda <- bc$x[which.max(bc$y)]
FLI$Local_Trips1 <- (((FLI$Local_Trips)^lambda - 1) / lambda)
new_model <- lm(FLI$Local_Trips1 ~ FLI$Influenza_Deaths)
summary(new_model)
qqnorm(new_model$residuals)
qqline(new_model$residuals)
plot(FLI$Local_Trips1 ~ FLI$Influenza_Deaths)
abline(new_model)
conf_intervals <- confint(new_model, level = 0.95)
print(conf_intervals)
```

Florida Covid Deaths vs Interstate Trips
```{r}
model <- lm(FL$Interstate_Trips ~ FL$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Florida Covid Deaths vs Interstate Travel")
qqline(model$residuals) 
FL$CookD = cooks.distance(model) 
FLC <- FL[which(FL$CookD < 0.5),]
bc <- boxcox(FLC$Interstate_Trips ~ FLC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
FLC$Interstate_Trips1 <- (((FLC$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(FLC$Interstate_Trips1 ~ FLC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(FLC$Interstate_Trips1 ~ FLC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals) 
```

Florida Influenza Deaths vs Interstate Trips
```{r}
model <- lm(FL$Interstate_Trips ~ FL$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Florida Influenza Deaths vs Interstate Travel") 
qqline(model$residuals) 
FL$CookD = cooks.distance(model) 
FLI <- FL[which(FL$CookD < 0.5),] 
bc <- boxcox(FLI$Interstate_Trips ~ FLI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
FLI$Interstate_Trips1 <- (((FLI$Interstate_Trips)^lambda - 1) / lambda) 
new_model <- lm(FLI$Interstate_Trips1 ~ FLI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(FLI$Interstate_Trips1 ~ FLI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

Florida Covid Deaths vs Long Distance Trips
```{r}
model <- lm(FL$Long_Distance_Trips ~ FL$Covid_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Florida Covid Deaths vs Long_Distance Travel")
qqline(model$residuals) 
FL$CookD = cooks.distance(model) 
FLC <- FL[which(FL$CookD < 0.5),]
bc <- boxcox(FLC$Long_Distance_Trips ~ FLC$Covid_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
FLC$Long_Distance_Trips1 <- (((FLC$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(FLC$Long_Distance_Trips1 ~ FLC$Covid_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(FLC$Long_Distance_Trips1 ~ FLC$Covid_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals) 
```

Florida Influenza Deaths vs Long Distance Trips
```{r}
model <- lm(FL$Long_Distance_Trips ~ FL$Influenza_Deaths) 
qqnorm(model$residuals, main = "Normal Q-Q Plot of Florida Influenza Deaths vs Long_Distance Travel") 
qqline(model$residuals) 
FL$CookD = cooks.distance(model) 
FLI <- FL[which(FL$CookD < 0.5),] 
bc <- boxcox(FLI$Long_Distance_Trips ~ FLI$Influenza_Deaths) 
lambda <- bc$x[which.max(bc$y)] 
FLI$Long_Distance_Trips1 <- (((FLI$Long_Distance_Trips)^lambda - 1) / lambda) 
new_model <- lm(FLI$Long_Distance_Trips1 ~ FLI$Influenza_Deaths) 
summary(new_model) 
qqnorm(new_model$residuals) 
qqline(new_model$residuals) 
plot(FLI$Long_Distance_Trips1 ~ FLI$Influenza_Deaths) 
abline(new_model) 
conf_intervals <- confint(new_model, level = 0.95) 
print(conf_intervals)
```

